### 2011-12-14 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: In progress.

According to \cite{Mlynkova:2008:AAX:1494650.1495496}, the type of the inference method can be divided into \emph{heuristic} and \emph{grammar-inferring}. Heuristic methods \cite{Chidlovskii:2002:SEX:544220.544288, Garofalakis:2000:XSE:342009.335409, Moh:2000:RSW:336597.336638, Wong03onstructural, Vosta:2008:EAC:1802514.1802522} are based on experience with manual construction of schemas, motivated by real-world usages of XML schema, and their result commonly does not belong to any class of grammar. Two of these approaches are described in Section \ref{section_xtract} and Section \ref{section_even_an_ant_can_create_an_xsd}. \todo{chce to větu proč zrovna dva}

@@

\todo{Tato věta hodně divná.} In the second step, assuming a correct schema it is wanted to specialize the regular expressions involved in the schema with regard to the XML documents, resulting in more precise and readable schema. Optional substeps are pruning of unused schema fragments, correction of lower and upper bounds of occurrences, transcription of operators to a more restrictive but simplier form, if this transcription preserves the validity, and refactorization to improve readability.

@@

The pattern occurrence is considered of case (O1) if it is the for join pattern (weight: 1), if aggregation function \texttt{avg}, \texttt{min}, \texttt{max} or \texttt{sum} is applied on a return path (weight: 1) or if aggregation function \texttt{count} is applied on a return path (weight: 0.75). \todo {Q: definovat return path? A: no, možná spíš jednu větu co to zhruba je}

>>>>

According to \cite{Mlynkova:2008:AAX:1494650.1495496}, the type of the inference method can be divided into \emph{heuristic} and \emph{grammar-inferring}. Heuristic methods \cite{Chidlovskii:2002:SEX:544220.544288, Garofalakis:2000:XSE:342009.335409, Moh:2000:RSW:336597.336638, Wong03onstructural, Vosta:2008:EAC:1802514.1802522} are based on experience with manual construction of schemas, motivated by real-world usages of XML schema, and their result commonly does not belong to any class of grammar. Two of these approaches are described in Section \ref{section_xtract} and Section \ref{section_even_an_ant_can_create_an_xsd}. The former one incorporates so-called MDL principle to create the (sub)optimal result. The latter one combines several verified methods together to improve the quality of the result.

@@

In the second step, regular expressions from the corrected schema are specialized with regard to the XML documents, resulting in a more precise and readable schema. Optional substeps are pruning of unused schema fragments, correction of lower and upper bounds of occurrences, transcription of operators to a more restrictive but simplier form, if this transcription preserves the validity, and refactorization to improve readability.

@@

The pattern occurrence is considered of case (O1) if it is the for join pattern (weight: 1), if aggregation function \texttt{avg}, \texttt{min}, \texttt{max} or \texttt{sum} is applied on a target return path (weight: 1) or if aggregation function \texttt{count} is applied on a target return path (weight: 0.75), where target return paths are paths in $C_R$ starting with $\$e_2$.

### 2011-12-14 doc/theses/mikula/diplomka.tex
Master thesis: Corrections.
Master thesis: In progress.

%% Ostatní balíčky
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amssymb}
%\usepackage{alltt}
\usepackage{todonotes}
\usepackage{algorithmic}
\usepackage[chapter]{algorithm}

@@

%%% Jednotlivé kapitoly práce jsou pro přehlednost uloľeny v samostatných souborech
\chapter{Úvod}
\todo[inline]{TODO}
\chapter{Použité technologie/pojmy}
\todo[inline]{TODO}
Krátce popsat co je XML Schema, DTD, XPath, XQuery, možná ňejaký automat apod. Prostě co budete dále v textu potřebovat. Skratky: XSD, ...

\include{analysis_of_recent_approaches}
\include{analysis_of_xquery}
%\include{kap2}
%\include{kap3}

@@

%%% Seznam pouľité literatury
\nocite{*}
\bibliographystyle{plain}
\bibliography{literature}

>>>>

%% Ostatní balíčky
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amssymb}
%\usepackage{alltt}
\usepackage{todonotes}
\usepackage{algorithmic}
\usepackage[chapter]{algorithm}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{threeparttable}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage[chapter]{algorithm}

@@

%%% Jednotlivé kapitoly práce jsou pro přehlednost uloľeny v samostatných souborech
\include{introduction}
\include{used_technologies_and_definitions}
\include{analysis_of_recent_approaches}
\include{analysis_of_xquery}
\include{pre_creation_of_algorithm}
\include{proposed_algorithm}
%\include{kap3}

@@

%%% Seznam pouľité literatury
\nocite{*}
\bibliographystyle{plain}
\todo[inline]{Literatura tady určitě co nejpodrobněji - odkaz nestačí, za měsíc nemusí existovat. A nemělo by to přetékat okraj.}
\todo[inline]{Literatura - jInfer modules documentation - Tady by neškodily odkazy na jednotlivé dokumenty.}
\bibliography{literature}

### 2011-12-14 doc/theses/mikula/introduction.tex
Master thesis: In progress.

Despite an conveyed encouragement to use an XML schema along with an XML data representation, in practise it is done sparsely. Commonly, XML documents are not assigned with their respective XML schema at all or the schema is outdated due to modifications done to a structure of data without updating the schema. \todo{ref na clanok s tvrdenim}

@@

\section{Aim of this Work}
Our aim is to perform a research on the problem of inference of an XML schema for the given set of XML data in a situation when we are provided also with a set of related operations (XML queries, XSLT scripts \todo{ref} etc.).

>>>>

Despite an conveyed encouragement to use an XML schema along with an XML data representation, in practise it is done sparsely. Commonly, XML documents are not assigned with their respective XML schema at all or the schema is outdated due to modifications done to a structure of data without updating the schema \cite{Mlynkova:2008:AAX:1494650.1495496}.

@@

\section{Aim of this Work}
Our aim is to perform a research on the problem of inference of an XML schema for the given set of XML data in a situation when we are provided also with a set of related operations (XML queries, XSLT scripts \cite{Clark:99:XTV} etc.).

### 2011-12-14 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

The syntactic analysis needs to be slightly modified to suit our case. It writes its result into a file in an XML representation. Instead, we need to keep the result in memory and pass it to consecutive steps of our algorithm. Though, this requirement concerns modifications of implementation while the core of the processing remains untouched. Therefore, we also do not describe these modifications.

\subsection{Description of the Syntax Tree}
Since we modified only the implementation of the output form, the design of the syntax tree remains consequent to the entire design of the analyses. Each node represents a logical component of a query. Inner nodes stand for XQuery constructs that are composed of other constructs and can be further divided. Examples of such constructs are $FLWOR$, $if-than-else$ and function call. Leaf nodes represents elements of XQuery language that can be devided no more. Typical representants are literal constants. \todo{zistit, ci konstanty nahodou nie su jedine}

@@

An important characteric of the syntax tree is related to a definition of local variables and their scope. The representation of a definition of a local variable is $VariableBinding$ node. Nodes of this type contain only two subnodes; a type of the variable and a binding expression. The node and the entire its subtree representing the type do not contain any expressions. The binding expression node is an expression node but the represented expression cannot use the variable which is just being bound. Therefore the scope of the new variable is not the subtree of the $VariableBinding$ node. Assuming the post-order numbering of the nodes, the new variable may be valid in some nodes with a higher post-order sequence number. Which nodes that are, it depends on the type of the ancestor node(s).

@@

\section{Step 2: Static Analysis of Expression Types}
In the second step, we try to statically (without evaluation of the queries) determine types of expressions in the syntax tree. Information on the types of expressions can be used by consecutive steps of the algorithm. The consecutive steps will probably not use the determined types of all expressions, however this step may be useful in a future extending.

We want to be able to capture the following types.

\begin{itemize}
\item XML Schema built-in atomic types \todo{link do appendixu}.
\item Type $xs:untyped$.
\item Type representing any item. \todo{je potrebne?}
\item Type representing an element, attribute, item, node, text node, comment, processing instruction, document node.
\item Type representing a set of elements or attributes selected by a certain path expression. The path expression is included in this type. Let this type be identified as $pathType$
\end{itemize}

\todo[inline]{Akeho typu je napr path expression /root/(elementA * 2)?}

@@

If we cannot determine the type of an expression we express that using $null$. Example of such case is path expression $/rootElement/(elementA * 2)$. \todo{Nejak dopisat}

@@

\todo[inline]{Este by sa dala urobit analyza volania funkcii, do ktorych su predavane nejake elementy/atributy o ktorych vieme ich path expression. Vysledkom tejto funkcie by totiz zas mohli byt elementy/atributy o ktorych vieme (pozmenenu) path expression a nie len nezname elementy/atributy.}

\subsection{Determination of Function Return Types}
Determination of return types of functions is needed because function calls can appear in expressions. However a return type of a function can be determined at the moment the analysis of expressions encounters a call of the function, it involves multiple transitions of the syntax tree in a search for a definition of a particular function.

@@

A simple algorithm is presented in \ref{ALG_determination_of_function_return_types} \todo{uvadzat aj taketo jednoduche funkcie?}. It uses \texttt{getFunctionDeclarationNodes()} function, which is not presented due to its simplicity. It returns a list of all function declaration nodes in the syntax three. Actually, it does not have to search the whole syntax tree as the function declaration nodes can be present only in the query prolog section.

For simplicity, we will focus on locally defined functions. We will not determine types of functions defined in other modules since the principle is similar but it is somewhat more difficult to implement \todo{je to ok?}. Return types of built-in functions are fixed, and thus, there is no need to analyze them.

@@

For the rest of the thesis, we assume function \texttt{getFunctionReturnType()} which takes a function name and returns the return type of the function if the function is either built-in or it is recorded in the associative array. Otherwise, \texttt{null} is returned.

@@

\subsection{Determination of Global Variable Types}
A similar approaches as in the case of functions can be applied to determine types of global variables. Alike the functions, the global variables are defined in the prolog section. A type of a variable can be explicitly specified in its definition \todo{je to tak? priklad}. If it is not it may often be deducible from the binding expression. Again, we do not analyse external variables for the same reason of simplicity as the external functions.

@@

The algorithm iterates through the variable declaration nodes from the prolog and if the variable is explicitly assigned with its type than the type is noted. Otherwise, an attempt of the type deduction of the expression is made. The deduction of the type from the expression is presented in \ref{ALG_func_determineExpressionType}. On input, it takes an expression node and types of local variables that are valid in the expression (also called context of variables or variable context). The presented algorithm is just shortened illustration since the complete version is too long to be presented in this text. Nevertheless, the principle is straightforward. Depending on the class of the expression, its type can be either determined directly or it depends on its subexpressions. \todo{link na mozne triedy vyrazov.}

Function $determineExpressionType()$ is called within function $analysisOfExpressionTypes$ presented in \ref{ALG_func_analysisOfExpressionTypes}, which recursively determines types of all subexpressions. Two important questions about this function emerge. How (in which order) are the tree nodes recursively processed and how does the function handle definitions (bindings) of new variables which may also appear in the expressions?

The order of the recursion is post-order. The reason is that an expression node may need to know types of its subexpressions to determine its own type and we want to determine types of all expressions. Therefore, using the post-order, subexpressions of an expression are processed first, and then the expression itself without any need for further recursion because the types of the subexpressions are already determined.

The handling of new variable definitions relies on the fact that the definitions make the new variables valid only in nodes with a higher sequence number when numbered in the post-order \todo{overit}. Therefore, the left-most subnode of a certain node can be processed without an extension of the variable context. And, if the left-most subnode extends the variable context for the following nodes in the post-order numbering, it can be easily handled because the types of the new variables can be directly determined since the binding expressions are already processed (thus, their types are known). Every node ''knows'' wheather or not it may define new variables for nodes with higher sequence numbers. This is expressed in the algorithm by the condition at line 10. This condition is double-checked at line 3 where it meaning is that every node even ''knows'' if its particular subnode may define new variables. An example is $FLWOR$ construct. The processing of $FLWOR$ knows that the first part (the first subnode) of this node may bind new variables using $for$ and $let$ constructs. After the subnode is processed, the processing of the $FLWOR$ node looks if any new variables were bound and if so the context of local variables is extended. This is done at line 4. Function $mergeContextVarTypes$ presented in \ref{ALG_function_mergeContextVarTypes} writes every record from its second argument (the new variables) into ist first argument (the variable context). If there are records for variables with the same names in the context, they are overwritten to correspond to the variable overlaping. It is important to note that we assume the variable context is not passed by refence but by value, and hence, the variable context of a certain node is not affected by the recursive processing of its subnodes.

@@

@@

Function $analysisOfExpressionTypes$ called upon a binding expression of a global variable determines the type of the binding expression, and hence, the type of the variable. In the case of global variables, the argument $contextVarTypes$ is empty because there are no local variables valid in the prolog section.

@@

The types of processed global variables are available trough function $getGlobalVariableType()$. If the function gets a variable that is not a global one, it returns $null$. Function $getVariableType()$ called in \ref{ALG_func_determineExpressionType} is defined in \ref{ALG_function_get_variable_type}. It checks if the specified variable is amongst the given local variables. If so, it returns its type, else it handles the variable as a global one and if such global variable does not exist the result is $null$.

@@

\section{Step 3: Inference of Built-in Types}
In this step, the algorithm goes through the syntax tree and tries to infer types of elements and attributes from expressions using the type information from the previous step. These two steps could be merged together but for better comprehension we present it separately.

How are the types inferred from the expression types? We do not exploit all expressions. Only expressions of a particular type are exploited. Specifically, an expression has to contain an subexpression $E$ of $pathType$ type (expression representing a certain element or attribute or set of elements or attributes). In the following text, the set represented by expression $E$ is denoted $S$. Another requirement is the expression has to be either a function call or an arithmetic operation \todo{Nejake ine ako napr type constructor, cast as? Princip je stale rovnaky}.

@@

\subsection{Function Calls}
This case is quite simple. The algorithm encounters a function call and one of the arguments is a known set of elements of attributes (subexpression $E$ representing $S$). To determine the type of $S$, it is only needed to determine the type of the corresponding formal argument from the definition of the function. The function is either a built-in one so its definition is known or it is defined in the prolog section. External functions are not processed as was mentioned already.

If the type $T$ of the formal argument is a built-in type or its sequence then $T$ is also the inferred type of $S$. Otherwise, no statement is inferred.

@@

>>>>

The syntactic analysis needs to be slightly modified to suit our case. It writes its result into a file in an XML representation. Instead, we need to keep the result in memory and pass it to consecutive steps of our algorithm. Though this requirement concerns modifications of implementation, the core of the processing remains untouched. Therefore, we also do not describe these modifications.

\todo[inline]{Toto vše je OK, ale asi budeme potřebovat vědět, co nám z té analýzy leze za informace se kterými dál pracujeme. Čili vstupy našeho algoritmu je potřeba popsat přesně, ideálně formálně, tj. je to asi nějaký strom T= (V, E), kde V je... atd. Jeslti už je to pak implementováno jako objekty v paměti nebo XML data je celkem jedno a bude popsáno v kapitola Implementation.}

\subsection{Description of the Syntax Tree}
Since we modified only the implementation of the output form, the design of the syntax tree remains consequent to the entire design of the analyses. Each node represents a logical component of a query. Inner nodes stand for XQuery constructs that are composed of other constructs and can be further divided. Examples of such constructs are $FLWOR$, $if-than-else$ and function call. Leaf nodes represent elements of XQuery language that cannot be further devided. Typical representants are literal constants. \todo{zistit, ci konstanty nahodou nie su jedine}

\todo[inline]{\^ Toto bude potřeba popsat přesně, ne jen příkladem. Klidně převezměnte z diplomky JS.}

@@

\todo[inline]{\^ Toto je skoro stejný odstavec ne?}

An important characteric of the syntax tree is related to a definition of local variables and their scope. The representation of a definition of a local variable is $VariableBinding$ node. Nodes of this type contain only two subnodes; a type of the variable and a binding expression. The node and its subtree representing the type do not contain any expressions. The binding expression node is an expression node but the represented expression cannot use the variable which is just being bound. Therefore the scope of the new variable is not the subtree of the $VariableBinding$ node. Assuming \todo{Toto je velmi high-level popis na to, jak málo o syntaktickém stromě a dalších položkách víme.} the post-order numbering of the nodes, the new variable may be valid in some nodes with a higher post-order sequence number. Which \todo{Toto není anglický slovosled.} nodes that are, it depends on the type of the ancestor node(s).

@@

\section{Step 2: Static Analysis of Expression Types}
In the second step, we statically (i.e. without evaluation of the queries) determine types of expressions in the syntax tree. Information on the types of expressions can be used by consecutive steps of the algorithm. The consecutive steps will not use the determined types of all expressions, however this step may be useful in a future extending.

\todo[inline]{Tady z těch try a probably je jasně vidět, že netušíte co vlastně přesně algoritmus bude dělat. Nejdříve si to rozmyslete, pak pište text. Rozhodně by se takové výrazy neměly v DP dobjevovat, působít o velmi nedůvěryhodně. Měl by to být strohý popis toho, co bylo uděláno.}

We want to capture the following types.

\begin{itemize}
\item XML Schema built-in atomic types \todo{link do appendixu}.
\item Type $xs:untyped$. \todo{to je co?}
\item Type representing any item. \todo{je potrebne?}
\item Type representing an element, attribute, item, node, text node, comment, processing instruction, document node.
\item Type representing a set of elements or attributes selected by a certain path expression. The path expression is included in this type. Let this type be identified as $pathType$.
\end{itemize}

\todo[inline]{Q: Akeho typu je napr path expression /root/(elementA * 2)? A: Datový typ je daný operátorem. Hodnota elementu se přetypuje.}

@@

If we cannot determine the type of an expression, we express that using $null$. An example of such case is path expression $/rootElement/(elementA * 2)$. \todo{Nejak dopisat}

@@

\todo[inline]{Este by sa dala urobit analyza volania funkcii, do ktorych su predavane nejake elementy/atributy o ktorych vieme ich path expression. Vysledkom tejto funkcie by totiz zas mohli byt elementy/atributy o ktorych vieme (pozmenenu) path expression a nie len nezname elementy/atributy.
A: Přesně tak. A jak říkám - není třeba vše co navrhnete implementovat.}

\subsection{Determination of Function Return Types}
Determination of return types of functions is needed because function calls can appear in expressions. A return type of a function can be determined at the moment the analysis of expressions encounters a call of the function, however, it involves multiple transitions of the syntax tree in a search for a definition of a particular function.

@@

A simple algorithm is presented in Algorithm \ref{ALG_determination_of_function_return_types} \todo{Q: uvadzat aj taketo jednoduche funkcie? A: Obecně by mělo být popsáno vše. Ale pokud se nějaká jednoduchá věc např. opakuje, tak stačí napsat, že je algoritmus podobný jako v předchozím případě nebo tak něco.}. It uses \texttt{getFunctionDeclarationNodes()} function, which returns a list of all function declaration nodes in the syntax three. Actually, it does not have to search the whole syntax tree as the function declaration nodes can be present only in the query prolog section.

For simplicity, we will focus on locally defined functions. We will not determine types of functions defined in other modules since the principle is similar but it is somewhat more difficult to implement \todo{Q: je to ok? A: No spíš napište něco jako without loss of generality.}. Return types of built-in functions are fixed and, thus, there is no need to analyze them.

@@

For the rest of the thesis, we assume function \todo{Většinou se na začátek sekce s algoritmem dává seznam používaných  funkcí a jejich význam.} \texttt{getFunctionReturnType()} which takes a function name and returns the return type of the function if the function is either built-in or it is recorded in the associative array. Otherwise, \texttt{null} is returned.

@@

\subsection{Determination of Global Variable Types}
A similar approach as in the case of functions can be applied to determine types of global variables. Alike the functions, the global variables are defined in the prolog section. A type of a variable can be explicitly specified in its definition \todo{je to tak? priklad}. If it is not, it may often be deducible from the binding expression. Again, we do not analyse external variables for the same reason as in case of external functions.

@@

\todo[inline]{algoritmus 6.2, riadok 2, slovo "represents" - Tady by neškodilo definovat nějakou funkci a její možné návratové hodnoty a toto používat.}
\todo[inline]{algoritmus 6.2, riadok 19 - Totéž, neškodila by nějaká funkce, tj. trochu formálnější zápis. Jednak se pravděpodobně bude hodit dál a druhak to zpřehlední popis.}

The algorithm iterates through the variable declaration nodes from the prolog and if the variable is explicitly assigned with its type, the type is noted. Otherwise, an attempt of the type deduction of the expression is made. The deduction of the type from the expression is presented in Algorithm \ref{ALG_func_determineExpressionType}. On input, it takes an expression node and types of local variables that are valid in the expression (also called context of variables or variable context). The presented algorithm is just shortened illustration since the complete version is too long to be presented in this text. Nevertheless, the principle is straightforward. Depending on the class of the expression, its type can be either determined directly or it depends on its subexpressions. \todo{link na mozne triedy vyrazov.}

Function $determineExpressionType()$ is called within function $analysisOfExpressionTypes$ presented in Algorithm \ref{ALG_func_analysisOfExpressionTypes}, which recursively determines types of all subexpressions. Two important questions about this function emerge. How (in which order) are the tree nodes recursively processed and how does the function handle definitions (bindings) of new variables which may also appear in the expressions?

The order of the recursion is post-order. The reason is that an expression node may need to know types of its subexpressions to determine its own type and we want to determine types of all expressions. Therefore, using the post-order, subexpressions of an expression are processed first, and then the expression itself without any need for further recursion, because the types of the subexpressions are already determined.

The handling of new variable definitions relies on the fact that the definitions make the new variables valid only in nodes with a higher sequence number when numbered in the post-order \todo{overit}. Therefore, the left-most subnode of a certain node can be processed without an extension of the variable context. And, if the left-most subnode extends the variable context for the following nodes in the post-order numbering, it can be easily handled because the types of the new variables can be directly determined since the binding expressions are already processed (thus, their types are known). Every node ''knows'' wheather or not it may define new variables for nodes with higher sequence numbers. This is expressed in the algorithm by the condition at line 10. This condition is double-checked at line 3 where its meaning is that every node even ''knows'' if its particular subnode may define new variables. An example is a $FLWOR$ construct. The processing of $FLWOR$ knows that the first part (the first subnode) of this node may bind new variables using $for$ and $let$ constructs. After the subnode is processed, the processing of the $FLWOR$ node looks if any new variables were bound and if so the context of local variables is extended. This is done at line 4. Function $mergeContextVarTypes$ presented in Algorithm \ref{ALG_function_mergeContextVarTypes} writes every record from its second argument (the new variables) into ist first argument (the variable context). If there are records for variables with the same names in the context, they are overwritten to correspond to the variable overlaping. It is important to note that we assume the variable context is not passed by refence but by value, and hence, the variable context of a certain node is not affected by the recursive processing of its subnodes.

@@

\todo[inline]{Algoritmus analysisOfEXpressionTypes, line 10 - Tady tyhle věty jsou v pseudoalgoritmech divné. Měy by se vyskytovat minimálně. JInak je to pak v podstatě jen odřádkovaná věta, ne formální popis algoritmu bez technických detailů.}

\todo[inline]{Pozor na to přetékání textu - na spoustě míst.}

@@

Function $analysisOfExpressionTypes$ called upon a binding expression of a global variable determines the type of the binding expression, and hence, the type of the variable. In case of global variables, the argument $contextVarTypes$ is empty, because there are no local variables valid in the prolog section.

@@

The types of processed global variables are available trough function $getGlobalVariableType()$. If the function gets a variable that is not a global one, it returns $null$. Function $getVariableType()$ called in Algorithm \ref{ALG_func_determineExpressionType} is defined in Algorithm \ref{ALG_function_get_variable_type}. It checks if the specified variable is amongst the given local variables. If so, it returns its type, else it handles the variable as a global one and if such global variable does not exist the result is $null$.

@@

\section{Step 3: Inference of Built-in Types}
In this step, the algorithm goes through the syntax tree to infer types of elements and attributes from expressions using the type information from the previous step. These two steps could be merged together but for better comprehension we present it separately.

How are the types inferred from the expression types? We do not exploit all expressions. Only expressions of a particular type are exploited. Specifically, an expression has to contain an subexpression $E$ of $pathType$ type (expression representing a certain element or attribute or set of elements or attributes). In the following text, the set represented by expression $E$ is denoted $S$. Another requirement is that the expression has to be either a function call or an arithmetic operation \todo{Q: Nejake ine ako napr type constructor, cast as? Princip je stale rovnaky. A: ak to jen popište. To je naprosto OK.}.

@@

\subsection{Function Calls}
This case is quite straightforward. The algorithm encounters a function call and one of the arguments is a known set of elements of attributes (subexpression $E$ representing $S$). To determine the type of $S$, it is only needed to determine the type of the corresponding formal argument from the definition of the function. The function is either a built-in one so its definition is known or it is defined in the prolog section. External functions are not processed as was mentioned already.

If the type $T$ of the formal argument is a built-in type or its sequence, then $T$ is also the inferred type of $S$. Otherwise, no statement is inferred.

@@

\todo[inline]{Pěkné, neškodilo by proložit příklady, tj. dotaz, strom, co z něho odvodíme.}
